Impact of interaction network structure on community-level plant reproduction success

### 2019-02-14 paper_round2.Rmd
paper half written

---
title: "Impact of interaction network structure on community-level plant reproduction success"
author: "Magrach, A, Molina, FP, Bartomeus, I"
date: "6 November 2018"
output: html_document
bibliography: library.bib
editor options:
  chunk_output_type: console
---

------------------------------------------------------------------------------------------------
To be potentially submitted to ECOLOGY LETTERS as a Letter: maximum of 5000 words and 6 figures, tables or text boxes. 
The abstract page should contain a short summary not exceeding 150 words for Letters.

@@

---------------------------------------------------------------------------------------------------------

@@

Declines in pollinator diversity and abundance have been reported across different regions, with implications for the reproductive success of many plant species. However, research has targeted the consequences for individual plant species, particularly focusing on pairwise plant-pollinator interactions, and largely overlooking community-level dynamics. Yet species do not interact in isolation, they are embedded within larger networks whose structure can affect pollinator functional roles and, ultimately, the pollination service they deliver to plants. Here, we present one of the first efforts linking pollinator visitation and plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems. We find that for prediction purposes, information on simple visitation metrics is sufficient. Contrastingly, a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on network structure.

@@

Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain differences found  across different plant individuals. Some have gone a step further by including information on the efficiency of these visits, thus adding a measure of quality to the pollination services (REF). Contrastingly, community-level analyses remain scarce [@Bennett2018]. Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species. We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Lazaro2014]. Understanding how changes in pollinator diversity affect whole plant assemblages is thus a major challenge that requires attention.

The few pollination studies that have analysed the effects of changing pollinator diversity for reproductive success at the community level, have done so using mainly experimental setups. As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but also they found that the structure that shaped the community had an important effect [@Frund2013]. In particular, these authors found that functional complementarity between pollinators, in terms of plant species and temperature coverage (a measure of the overlap in the use of plant resources and optimum temperature activity) had a positive effect for average seed set at the community level [@Frund2013]. This provides added information on the effects of biodiversity for ecosystem functioning, suggesting that not only the diversity of species present but also the diversity of roles and ways in which a community is structured are determinant factors.

Indeed, theoretical research has long suggested that the structure of a community has an effect for ecosystem functioning (reviewed in [@Thompson2012]). This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested with empirical data. Specifically, a major knowledge gap resides in understading which aspects of structure determine which aspects of function [@Thompson2012]. We are now at a point in which there is considerable understanding on the attributes of interaction networks (REF, REF, REF). Even further, we now have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016]. Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures (REF) or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004]. The time is thus ripe to use this knowledge to explore relationships between community structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.

Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level. To this end, we use a well-replicated dataset encompassing 16 well-resolved networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain. Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive succes.

@@

Within each site, we marked between 2 and 12 individuals (6.49 +- 2.37) of 1 to 6 plant species (4.06 +- 1.69), depending on availability and presence of flowers during the first sampling event. For each individual, we counted the number of flowers at the beginning of the season and recorded fruit set, the number of seeds per fruit (for 2-36 fruits, 11.17 +- 6.84) and average seed weight at the end of the season???. Our survey included a total of 19 plant species across our 16 sites.

@@

In order to analyse how differences within the pollinator community might affect plant reproductive success, we constructed weighted interaction networks by pooling the data for the 7 rounds of sampling. We thus obtained one weighted interaction network per site representing the frequency of visits by different pollinator species to different plant species. For each network we then proceeded to extract a series of relevant network metrics.

@@

At the species level, we focused on attributes defining the position of a focal plant species within the larger community. As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap between a focal species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality, which depicts the importance of the plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.

@@

Many network attributes vary with network size and complexity [@Bluthgen2006]. In the case of nestedness, we know it can be affected by network size and connectance (REF). An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks. However, this approach has been recently shown to present the same issues, as z-scores also change with network size and connectance [@Song2017]. Given the dependence of nestedness on network size and connectance, we followed the advice of these researchers by using a normalized value of nestedness, NODFc, which is independent of network size and thus comparable across different networks [@Song2017]. All network metrics were calculated using package bipartite [@Dormann2009].

@@

In order to evaluate whether adding information on community structure improves our ability to explain differences in reproductive success both at the species and the community level, we used general linear (GLM) and general linear mixed models (GLMM). In both cases (species and community-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2, that additionally included information on community structure.

At the species level, model 1 included as explanatory variables the diversity of pollinator species visiting a focal plant and the total number of visits received by that plant species; while model 2, added the two network attributes calculated at the species level: average niche overlap and centrality. In this case, we included plant species nested within site as a random effect to account for non-independence of several individuals measured for the same plant species within each site. The diversity of pollinator species visiting a focal plant was approximated using the plant´s normalised degree, i.e., the number of links with different pollinator species a plant has, scaled by the number of possible partners [@Dormann2009].

At the community level, we upscaled our species-level analyses. In this case, model 1 included total pollinator diversity and the total number of visits received by all plants within the community as explanatory variables. Model 2, in turn, added information on community structure by including nestedness and functional complementarity as explanatory variables.

Average values of reproductive success at the community level can be driven to a large extent by one single plant species. Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” in reproductive success across the whole community. We therefore calculated a measure of equity in reproductive success at the community level as the proportion of plant species within a site that is at 50% of the maximum value of fruitset recorded for that plant species within our sampling. We repeated this using 25% and 75% thresholds. We then used the same framework as before and fit the same model 1 and model 2 as those used at the community level but using equity in reproductive success as the response variable.

We used information criterion methods to find the best model for each case and selected the ones with the lowest Akaike Information Criterion (AIC) value. Differences in AIC values < 2, were not considered enough to select one model over the other.

@@

Finally, we tested whether the effect of community structure metrics increases with the number of plant species whose reproductive success is being considered. We expect that when only one plant species is considered, then the effect of community structure will be negligible. Further, we expect this effect to increase in importance as more plant species are considered (up to a maximum number of 6 species which is the maximum we have measured in our study).

To test this, we ran a simple simulation in which the number of species increases randomly (increases randomly or the identity of the sps is selected at random???) at each time step and calculate equity in reproductive success. Instead of drawing plants randomly for each run, for each plant number level and network, we test all possible combinations, as this number is low (n = 63 possible combiations overall for the network with the largest dataset) and increasing sampling events in our simulation would only result in repeated combinations. Then, we test the overall relation between equity in reproductive success and both community-level network metrics we consider: nestedness and functional complementarity within our simulated communities. To this end, for each species number level, we randomly combine the generated equity values across the 16 communities as to obtain one random value per species. Finally, for each of such combinations we calculated the estimate of equity in relation with functional complementarity and average all estimates from 1000 simulated combinations per number of plants considered. We expect that the more plants considered, the larger the resulting average estimates will be. Note that we only interpret the mean effects, as the variance among different plant number of species depends on the initial number of combinations.

@@

Within our sampling we recorded 57 species of plants and 277 species of pollinators. Within the pollinator community XX% of species were solitary bees, XX% hoverflies and XX%% other??

@@

library(citr) #to include citations. use addins to insert references

#First attempt to load the data, etc...

#prepare stuff-----
#If you don't have devtools install it
#install.packages("devtools")
#library(devtools)
#Then install the data package. Reprot issues 
#install_github("ibartomeus/BeeFunData", ref = "fun")
library(BeeFunData)
library(plyr)

@@

#write.csv(f.inds, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/plantindspersite.csv", row.names = FALSE)

@@

#write.csv(f.sps, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/plantspspersite.csv", row.names = FALSE)

@@

#write.csv(s.fruitnum, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/fruitnumberperplantindspersite.csv", row.names = FALSE)

@@

outsp.pl.site<-read.csv("SITE_plant_species_level_metrics.csv")
outsp.site<-read.csv("SITE_species_level_metrics.csv")
out.site<-read.csv("SITE_network_level_metrics.csv")

#####################################################################################################################
########################CALCULATE SAMPLING COMPLETENESS FOR POLLINATORS, PLANTS AND LINKS #############################
######################################################################################################################

@@

At the species level, our results show that for all measures of reproductive success considered (i.e., fruitset, number of seeds per fruit, fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only includes simple visitation metrics (i.e., the diversity of visiting pollinators and the total number of visits received by a focal plant species). In the case of fruitset, we find a positive effect of the diversity of species visiting a focal plant species (measured using the species´normalised degree, Fig. XX). Contrastingly, for seed set, fruit and seed weight we find that none of the variables included within our model explain the differences observed.

@@

@@

#head(out.site)
#str(out.site)
c<-cor(out.site[,2:20])
c2<-round(c,digits=2)
#write.csv(c2, file= "~/Dropbox/Beefun/Beefun/functioning/tables/variable_correlations.csv", row.names = TRUE, sep = ",")

@@

#write.csv(tableSx, file= "C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/plantindspersite.csv", row.names = FALSE, sep = ",")

@@

#calculate total number of visits per plant sps
d.vis<-ddply(d, c("Site_ID", "Plant_gen_sp"), summarise,
            tot.visits= sum(Frequency))

@@

 m1<-glmer(tot.fruitset ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=f2_scaled)

@@

 m2<-glmer(tot.fruitset ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="gaussian", data=f2_scaled)

 summary(m2)

@@

AICtab(m1, m2)

@@

# extract coefficients and p-values for m1 and present them in paper
coefs.m1 <- data.frame(coef(summary(m1)))
# use normal distribution to approximate p-value
coefs.m1$p.z <- 2 * (1 - pnorm(abs(coefs.m1$t.value)))
coefs.m1
summ<-round(coefs.m1,digits=2)
#write.csv(summ, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsfruitsetSPECIES.csv", row.names = TRUE)

#best model is m1, plot significant variable, in this case degree

pl1<-ggplot(f2_scaled,  aes(x=norm_degree.sc, y=tot.fruitset, color=Plant.sp)) +    
        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
        #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
        xlab("Normalized degree") +      
        ylab("Fruitset") + theme_bw()  + theme (legend.position= c(0.85,0.3)) +
        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + labs(col="Plant species") +  theme(legend.text = element_text(size = 10, face = "italic"), legend.title = element_text(size=11, face = "bold"))

pl1

#no color for different species

pl1b<-ggplot(f2_scaled,  aes(x=norm_degree.sc, y=tot.fruitset)) +    
        geom_point(size=4, color = "darkgrey") + geom_smooth(method=lm,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
        #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
        xlab("Normalized degree") +      
        ylab("Fruitset") + theme_bw()  + theme (legend.position= "none") +
        theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold"))

pl1b

##ahora con seed set

@@

AICtab(m1.seed, m2.seed)

@@

# extract coefficients and p-values for m1 and present them in paper
coefs.m1.seed <- data.frame(coef(summary(m1.seed)))
# use normal distribution to approximate p-value
coefs.m1.seed$p.z <- 2 * (1 - pnorm(abs(coefs.m1.seed$t.value)))
coefs.m1.seed
summ.seed<-round(coefs.m1.seed,digits=2)
#write.csv(summ.seed, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsseedsetSPECIES.csv", row.names = TRUE)

#SEED WEIGHT

m1.seed.w<-glmer(mean.seedw ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s3_scaled)

@@

vif(m1.seed.w)

m2.seed.w<-glmer(mean.seedw ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s3_scaled)

@@

vif(m2.seed.w)

@@

# extract coefficients and p-values for m1 and present them in paper
coefs.m1.seed.w <- data.frame(coef(summary(m1.seed.w)))
# use normal distribution to approximate p-value
coefs.m1.seed.w$p.z <- 2 * (1 - pnorm(abs(coefs.m1.seed.w$t.value)))
coefs.m1.seed.w
summ.seed.w<-round(coefs.m1.seed.w,digits=2)
#write.csv(summ.seed.w, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsseedweightSPECIES.csv", row.names = TRUE)

@@

m1.fruit.w<-glmer(mean.fruitweight ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s3_scaled)

@@

vif(m1.fruit.w)

m2.fruit.w<-glmer(mean.fruitweight ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="gaussian", data=s3_scaled)

@@

vif(m2.fruit.w)

@@

# extract coefficients and p-values for m1 and present them in paper
coefs.m1.fruit.w <- data.frame(coef(summary(m1.fruit.w)))
# use normal distribution to approximate p-value
coefs.m1.fruit.w$p.z <- 2 * (1 - pnorm(abs(coefs.m1.fruit.w$t.value)))
coefs.m1.fruit.w
summ.fruit.w<-round(coefs.m1.fruit.w,digits=2)
#write.csv(summ.seed.w, file="C:/Users/ainhoa.magrach/Dropbox/Beefun/Beefun/functioning/tables/resultsfruitweightSPECIES.csv", row.names = TRUE)

@@

### Network-level analyses

>>>>

---
title: "Impact of interaction network structure on community-level plant reproduction success"
author: "Magrach, A, Molina, FP, Bartomeus, I"
date: "6 November 2018"
output: html_document
bibliography: library.bib
csl: ecology-letters.csl
editor options:
  chunk_output_type: console
---

------------------------------------------------------------------------------------------------
[To be potentially submitted to ECOLOGY LETTERS as a Letter: maximum of 5000 words and 6 figures, tables or text boxes. 
The abstract page should contain a short summary not exceeding 150 words for Letters.

@@

@@

Declines in pollinator diversity and abundance have been reported across different regions, with implications for the reproductive success of many plant species. However, research has targeted the consequences for individual plant species, particularly focusing on pairwise plant-pollinator interactions, and largely overlooking community-level dynamics. Yet species do not interact in isolation, they are embedded within larger networks whose structure can affect pollinator functional roles and, ultimately, the pollination services they deliver to plants. Here, we present one of the first efforts linking pollinator visitation to plant reproduction from a community-wide perspective using a well-replicated dataset encompassing 16 well-resolved networks and data on reproductive success for 19 plant species from Mediterranean shrub ecosystems. We find that, for prediction purposes, information on simple visitation metrics is sufficient. Contrastingly, a mechanisitic understanding of the pathways through which differences in pollinator diversity translate into changes in reproductive success, requires additional information on network structure.

@@

Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain differences found  across different plant individuals. Some have gone a step further by including information on the efficiency of these visits, thus adding a measure of quality to the pollination services (REF). Contrastingly, community-level analyses remain scarce [@Bennett2018]. Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species. We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Lazaro2014]. Understanding how changes in pollinator diversity affect whole community assemblages is thus a major challenge that requires attention.

The few pollination studies that have analysed the effects of changing pollinator diversity for reproductive success at the community level, have done so using mainly experimental setups. As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but also they found that the structure that shaped the community had an important effect [@Frund2013]. In particular, these authors found that the functional complementarity between pollinators, in terms of plant species and temperature coverage (a measure of the overlap in the use of plant resources and optimum temperature activity) had a positive effect for average seed set at the community level [@Frund2013]. This provides added information on the effects of biodiversity for ecosystem functioning, suggesting that not only the diversity of species present but also the diversity of roles and ways in which a community is structured are determinant factors.

Indeed, theoretical research has long suggested that the structure of a community has an effect for ecosystem functioning (reviewed in [@Thompson2012]). This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data. Specifically, a major knowledge gap resides in understading which aspects of structure determine which aspects of function [@Thompson2012]. We are now at a point in which there is considerable understanding on the attributes of interaction networks (REF, REF, REF). Even further, we now have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016]. Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures (REF) or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004]. The time is thus ripe to use this knowledge to explore relationships between community structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.

Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level. To this end, we use a well-replicated dataset encompassing 16 well-resolved networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain. Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success.

@@

Within each site, we marked between 2 and 12 individuals (6.49 +- 2.37) of 1 to 6 plant species (4.06 +- 1.69), depending on the availability and presence of flowers during the first sampling event. For each individual, we counted the number of flowers at the beginning of the season and recorded fruit set, the number of seeds per fruit (for 2-36 fruits, 11.17 +- 6.84) and average seed weight at the end of the season???. Our survey included a total of 19 plant species across our 16 sites.

@@

In order to analyse how differences within the pollinator community might affect plant reproductive success, we constructed weighted interaction networks by pooling the data for the 7 rounds of sampling. We thus obtained one weighted interaction network per site, representing the frequency of visits by different pollinator species to different plant species. For each network, we then proceeded to extract a series of relevant network metrics.

@@

At the species level, we focused on attributes defining the position of a focal plant species within the larger community. As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap between a focal plant species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality, which depicts the importance of the plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.

@@

Many network attributes vary with network size and complexity [@Bluthgen2006]. In the case of nestedness, we know it can be affected by network size and connectance (REF). An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks. However, this approach has been recently shown to present the same issues, as z-scores also change with network size and connectance [@Song2017]. Given the dependence of nestedness on network size and connectance, we followed the advice of these researchers by using a normalized value of nestedness, NODFc, calculated as XXXX, where XXXXX [INCLUDE FORMULA AND DEFINE CONCEPTS], which is independent of network size and thus comparable across different networks [@Song2017]. All network metrics were calculated using package bipartite [@Dormann2009].

@@

In order to evaluate whether adding information on community structure improves our ability to explain differences in reproductive success - both at the species and the community level - we used general linear (GLMs) and general linear mixed models (GLMMs). In both cases (species and community-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2, that additionally included information on community structure.

At the species level, model 1 included as explanatory variables the diversity of pollinator species visiting a focal plant and the total number of visits received by that plant species; while model 2, added the two network attributes calculated at the species level: average niche overlap and centrality. In this case, we included plant species nested within site as a random effect to account for the non-independence of several individuals measured for the same plant species within each site. The diversity of pollinator species visiting a focal plant was approximated using the plant´s normalised degree, i.e., the number of links with different pollinator species a plant has, scaled by the number of possible partners [@Dormann2009].

At the community level, we upscaled our species-level analyses. In this case, model 1 included total pollinator diversity and the total number of visits received by all plants within the community as explanatory variables. Model 2, in turn, added information on community structure by including nestedness and functional complementarity as explanatory variables. As response variable we had the average reproductive success for the whole community (i.e., average fruitset, average number of seeds per fruit previously scaled for each species, average fruit and seed weight). We thus, had a single value per site and no random effects are needed in this case.

Average values of reproductive success at the community level can be driven to a large extent by a single plant species. Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” in reproductive success across the whole community. We therefore calculated a measure of equity in reproductive success at the community level as the proportion of plant species within a site that is at 50% of the maximum value of fruitset recorded for that plant species within our sampling. We repeated this using 25% and 75% thresholds. We then used the same framework as before and fit the same models 1 and 2 as the ones used at the community level, but using equity in reproductive success as the response variable.

We used information criterion methods to find the best model for each case and selected the ones with the lowest Akaike Information Criterion (AIC) value. Differences in AIC values < 2, were not considered enough to select one model over the other [@Burnham2011].

@@

Finally, we tested whether the importance of community structure in explaining differences in reproductive success increases with the number of plant species being considered. We expect that when only one plant species is considered, then the importance of community structure will be negligible, while we expect this importance to increase as more plant species are considered (up to a maximum number of 6 species which is the maximum we have measured in our study at a particular site).

To test this, we ran a simple simulation in which the number of species increased randomly at each time step and calculated equity in reproductive success. Instead of drawing plants randomly for each run, we tested all possible combinations for each plant number level and network, as this number is low (n = X x X = 63 possible combiations overall for the network with the largest dataset). Increasing sampling events in our simulation would only result in repeated combinations. Then, we tested the overall relationship between equity in reproductive success and both community-level network metrics we measured: nestedness and functional complementarity within our simulated communities. To this end, for each species number level, we randomly combined the generated equity values across the 16 communities as to obtain one random value per species. Finally, for each of such combinations we extracted the model estimate from a linear model relating equity in relation with functional complementarity and averaged all estimates from 1,000 simulated combinations per number of plants considered. We expect that the more plants considered, the larger the resulting average estimates will be. Note that we only interpret the mean effects, as the variance among different plant number of species depends on the initial number of combinations.

@@

Within our sampling we recorded `r nrow(d)` pollinator individuals belonging to 57 species of plants and 277 species of pollinators. Within the pollinator community XX% of species were solitary bees, XX% hoverflies, 20% honeybees, and XX%% other??

@@

#prepare stuff-----
#If you don't have devtools install it
#install.packages("devtools")
#library(devtools)
#Then install the data package. Reprot issues 
#install_github("ibartomeus/BeeFunData", ref = "fun")
library(BeeFunData)

#devtools::install_github("jonocarroll/mathpix") #package to include mathematical formulas
library(mathpix)

@@

#write.csv(f.inds, file="tables/plantindspersite.csv", row.names = FALSE)

@@

#write.csv(f.sps, file="tables/plantspspersite.csv", row.names = FALSE)

@@

#write.csv(s.fruitnum, file="tables/fruitnumberperplantindspersite.csv", row.names = FALSE)

@@

outsp.pl.site<-read.csv("SITE_plant_species_level_metrics.csv")
outsp.site<-read.csv("SITE_species_level_metrics.csv")
out.site<-read.csv("SITE_network_level_metrics.csv")
```

#######CALCULATE SAMPLING COMPLETENESS FOR POLLINATORS, PLANTS AND LINKS

@@

At the species level, our results show that in the case of fruitset, both model 1 and model 2 are equally good in explaining the variability observed (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other. This is despite the fact that model 2 has a greater number of variables and should be penalized for the added complexity it represents. We will thus comment results only for model 2, which in the case of fruitset shows a positive effect of the diversity of species visiting a focal plant species (measured using the species´normalised degree, Fig. XX) as well as a positive effect of the centrality of the focal plant on its fruitset.

@@

library(ggplot2)
library(grid)

@@

#head(out.site)
#str(out.site)
c<-cor(out.site[,2:20])
c2<-round(c,digits=2)
#write.csv(c2, file= "tables/variable_correlations.csv", row.names = TRUE, sep = ",")

@@

#write.csv(tableSx, file= "tables/plantindspersite.csv", row.names = FALSE, sep = ",")

@@

#calculate total number of visits per plant sps

d.vis<-ddply(d, c("Site_ID", "Plant_gen_sp"), summarise,
            tot.visits= sum(Frequency))

@@

 m1<-glmer(tot.fruitset ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2_scaled)

@@

 m2<-glmer(tot.fruitset ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID) + (1|Site_ID), family="binomial", data=f2_scaled)

 summary(m2) #both norm degree and weigh closeness have intervals not overlapping 0

@@

AICtab(m1, m2) #both are equally good using binomial distribution!!

@@

# extract coefficients and p-values for m1 and present them in paper
coefs.m2 <- data.frame(coef(summary(m2)))
# use normal distribution to approximate p-value
coefs.m2$p.z <- 2 * (1 - pnorm(abs(coefs.m2$z.value)))
coefs.m2
summ<-round(coefs.m2,digits=2)
#write.csv(summ, file="tables/resultsfruitsetSPECIES.csv", row.names = TRUE)

#both models equally good, plot significant variables, in this case degree, do partial residual plots to show the effect of that variable in isolation of the others

#devtools::install_github("hohenstein/remef")  USE THIS PACKAGE TO DO PARTIAL RESIDUAL PLOTS OF SIGNIFICANT VARIABLES

library(remef)
y_partial_norm <- remef(m2, fix= c( "tot.visits.sc", "weigh_closeness.sc", "niche.overlap.sc"), ran = "all", inverse = F)
#With this we remove the influece of x2 and the random effects from the dependent variable
y_partial_norm_inv<-exp(y_partial_norm)/(1+exp(y_partial_norm))
#then we use this new variable to plot. We use m1@frame as dataset because not all observations are used in modeldue to presence of NAs

pl1<-ggplot(m2@frame,  aes(x=m2@frame$norm_degree.sc[1:325,1], y=y_partial_norm_inv)) +    
  geom_point(size=4) + stat_smooth(method=lm,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
  xlab("Normalized degree") +      
  ylab("Fruitset") + theme_bw()  + theme (legend.position= c(0.85,0.3)) +
  theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + 
  labs(col="Plant species") +  theme(legend.text = element_text(size = 10, face = "italic"), legend.title = element_text(size=11, face = "bold"))

#pl1

y_partial_weigh <- remef(m2, fix= c( "tot.visits.sc", "norm_degree.sc", "niche.overlap.sc"), ran = "all", inverse = F)
#With this we remove the influece of x2 and the random effects from the dependent variable
y_partial_weigh_inv<-exp(y_partial_weigh)/(1+exp(y_partial_weigh))

pl1b<-ggplot(m2@frame,  aes(x=m2@frame$weigh_closeness.sc[1:325,1], y=y_partial_weigh_inv)) +    
  geom_point(size=4) + stat_smooth(method=lm,  size=1.5, se=TRUE, color = "black", alpha=0.2) + 
  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
  xlab("Centrality") +      
  ylab("Fruitset") + theme_bw()  + theme (legend.position= c(0.85,0.3)) +
  theme(text = element_text(size = 20), axis.text=element_text(size=rel(1.2)), axis.title=element_text(size=rel(1.3), face="bold")) + 
  labs(col="Plant species") +  theme(legend.text = element_text(size = 10, face = "italic"), legend.title = element_text(size=11, face = "bold"))

#pl1b

library(cowplot)
plot_grid(pl1, pl1b, labels = c("A", "B"))

Figure X. Partial residual plots showing the effect of a) pollinator species diversity (approximated using normalized degree) and b) species centrality on fruitset for each of the plant species considered. Dots represent each of the individuals sampled for each species within each site.

For all other measures of reproductive success considered (i.e., the number of seeds per fruit, fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only included simple visitation metrics (in this case, the diversity of visiting pollinators and the total number of visits received by a focal plant species). In this case, we find that none of the variables included within our model explain the differences observed.

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
##ahora con seed set

@@

AICtab(m1.seed, m2.seed) #m1 here is best model with m2 having a differnce of 4. However m2 has niche overlap as significant.

@@

# extract coefficients and p-values for m1 and present them in paper
coefs.m1.seed <- data.frame(coef(summary(m1.seed)))
# use normal distribution to approximate p-value
coefs.m1.seed$p.z <- 2 * (1 - pnorm(abs(coefs.m1.seed$t.value)))
coefs.m1.seed
summ.seed<-round(coefs.m1.seed,digits=2)
#write.csv(summ.seed, file="tables/resultsseedsetSPECIES.csv", row.names = TRUE)

#SEED WEIGHT
library(glmmTMB)
m1.seed.w<-glmmTMB(mean.seedw ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)

@@

m2.seed.w<-glmmTMB(mean.seedw ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)

@@

@@

# extract coefficients and p-values for m1 and present them in paper
summ.seed.w<-summary(m1.seed.w)$coefficients$cond
#write.csv(summ.seed.w, file="tables/resultsseedweightSPECIES.csv", row.names = TRUE)

@@

m1.fruit.w<-glmmTMB(mean.fruitweight ~  norm_degree.sc + tot.visits.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)

@@

m2.fruit.w<-glmmTMB(mean.fruitweight ~  norm_degree.sc  + tot.visits.sc + weigh_closeness.sc + niche.overlap.sc  + (1|Plant.sp:Site_ID), family="poisson", data=s3_scaled)

@@

@@

# extract coefficients and p-values for m1 and present them in paper
summ.fruit.w<-summary(m1.fruit.w)$coefficients$cond
#write.csv(summ.seed.w, file="tables/resultsfruitweightSPECIES.csv", row.names = TRUE)

@@

### Community-level analyses

At the network level, we find different patterns for fruitset and the number of seeds per fruit as compared to those for fruit and seed weight. In the case of fruitset and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed (i.e.,$\Delta AIC<2$). Again, because this suggests model 2 is a good model despite its added complexity we will comment results for this model only. In particular, we find that both fruitset and the number of seeds per fruit are positively related to functional complementarity between pollinators. Additionally, we find a negative effect of community-level pollinator species diversity on average fruitset.

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=10}

######################## NTW STRUCTURE ~ ECOSYSTEM FUNCTION
